Symmetric Circuits for Rank Gates

### 2018-02-13 sections/background.tex
FEB 13

Let $L$ be a logic and $\tau$ a vocabulary. For $\phi \in L[\tau]$ and a
sequence of variables $\vec{x}$, we write $\phi(\vec{x})$ if the free variables
in $\phi$ are among those in $\vec{x}$. Suppose $\vec{x} = (x_1, \ldots , x_k)$,
and let $\mathcal{A}$ be a $\tau$-structure with universe $U$, and let $\vec{a}
\in U^k$. We write $\mathcal{A} \models_L \phi[\vec{a}]$ if, and only if, $\phi$
is true in $\mathcal{A}$ with respect to $L$ where for all $i \in [k]$ each
variable $x_i$ is assigned to $a_i$. If the logic is obvious from context we
omit the subscript and just write $\mathcal{A} \models \phi[\vec{a}]$.

>>>>

Let $L$ be a logic and $\tau$ a vocabulary. For $\phi \in L[\tau]$ and a
sequence of variables $\vec{x}$, we write $\phi(\vec{x})$ if the free variables
in $\phi$ are among those in $\vec{x}$. Suppose $\vec{x} = (x_1, \ldots , x_k)$,
and let $\mathcal{A}$ be a $\tau$-structure with universe $U$. We call a
function $\alpha : {x_1, \ldots, x_k} \rightarrow U$ an \emph{assignment}. If
$\vec{a}\in U^k$, we write $\alpha^{\vec{x}}_{\vec{a}}$ to denote the assignment
that maps the variable $x_i$ to $a_i$ for $i \in [k]$. We say that two
assignments $\alpha$ and $\beta$ are \emph{compatible} if $\alpha$ and $\beta$
agree on the intersection of their domain. We write $\mathcal{A} \models_L
\phi[\alpha]$ if, and only if, $\phi$ is true in $\mathcal{A}$ with respect to
$L$ where for all $i \in [k]$ each variable $x_i$ is assigned to $\alpha(x_i)$.
If the logic is obvious from context we omit the subscript and just write
$\mathcal{A} \models \phi[\vec{a}]$.
